Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-06 ms/SI.Rmd
Don't hard-code bioregion lumping cutoff

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "inext_res",
  "redundancy_by_res",
  "redundancy_summary",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results",
  "japan_shp",
  "morans_i",
  "t_test_results",
  "aic_env_repro",
  "comm_ferns",
  "repro_data",
  "japan_pterido_tree",
  "model_fits_not_ult",
  "biodiv_ferns_cent",
  "protected_areas",
  "deer_range",
  "biodiv_ferns_spatial_lumped"
))
```

@@

```{r raw-lat, fig.width = 7, fig.height = 4}
# Convert spatial data frame to centroids with raw metrics
biodiv_ferns_cent_raw <- spatial_to_cent(
  biodiv_ferns_spatial,
  c("grids", "lat", "long", "richness", "pd_obs", "fd_obs"))

@@

```{r raw-biplot, fig.width = 7, fig.height = 7}
a <- ggplot(biodiv_ferns_spatial, aes(x = richness, y = pd_obs)) +
  geom_point(alpha = 0.5) +
  labs(x = "Richness", y = "PD")

@@

c <- ggplot(biodiv_ferns_spatial, aes(x = richness, y = fd_obs)) +
  geom_point(alpha = 0.5) +
  labs(x = "Richness", y = "FD")

@@

**`r s_figure("raw-biplot")`**. Relationships between observed functional and phylogenetic diversity and taxonomic richness in the ferns of Japan. (a), Phylogenetic diversity (PD). (b), Relative phylogenetic diversity (RPD). (c), Functional diversity (FD). (d), Relative functional diversity (RFD).

@@

# Map taxonomic clusters to grid cells
clusters_tax <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = taxonomic_cluster) %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster])

cluster_nodes_tax_tbl <- map_df(unique(clusters_tax$cluster), ~map_cluster_to_nodes(dendro_tax, clusters_tax, .)) %>%
  # Lump regions with just a few cells (3 or less)
  mutate(cluster = as.factor(cluster) %>% fct_lump_min(4))

@@

# Map phylogenetic clusters to grid cells
clusters_phy <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = phylo_cluster) %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster])

cluster_nodes_phy_tbl <- map_df(unique(clusters_phy$cluster), ~map_cluster_to_nodes(dendro_phy, clusters_phy, .)) %>%
  # Lump regions with just a few cells (3 or less)
  mutate(cluster = as.factor(cluster) %>% fct_lump_min(4))

>>>>

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "inext_res",
  "redundancy_by_res",
  "redundancy_summary",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results",
  "japan_shp",
  "morans_i",
  "t_test_results",
  "aic_env_repro",
  "comm_ferns",
  "repro_data",
  "japan_pterido_tree",
  "model_fits_not_ult",
  "biodiv_ferns_cent",
  "protected_areas",
  "deer_range",
  "biodiv_ferns_spatial_lumped",
  "bioregion_cutoff"
))
```

@@

```{r raw-lat, fig.width = 7, fig.height = 4}
# Convert spatial data frame to centroids with raw metrics, drop single high apomixis outlier
biodiv_ferns_cent_raw <- spatial_to_cent_for_model(
  biodiv_ferns_spatial,
  c("grids", "lat", "long", "richness", "pd_obs", "fd_obs"))

@@

```{r raw-biplot, fig.width = 7, fig.height = 7}
a <- ggplot(biodiv_ferns_spatial, aes(x = richness, y = pd_obs)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(x = "Richness", y = "PD")

@@

c <- ggplot(biodiv_ferns_spatial, aes(x = richness, y = fd_obs)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(x = "Richness", y = "FD")

@@

**`r s_figure("raw-biplot")`**. Relationships between observed functional and phylogenetic diversity and taxonomic richness in the ferns of Japan. (a), Phylogenetic diversity (PD). (b), Relative phylogenetic diversity (RPD). (c), Functional diversity (FD). (d), Relative functional diversity (RFD). Trendlines in (a, c) fit with general additive model using `r func("geom_smooth")` function in the `r pack("ggplot2")` R package [@Wickham2016].

@@

# Map taxonomic clusters to grid cells
clusters_tax <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = taxonomic_cluster)

cluster_nodes_tax_tbl <- map_df(unique(clusters_tax$cluster), ~map_cluster_to_nodes(dendro_tax, clusters_tax, .)) %>%
  # Lump regions with fewer grid-cells than cutoff
  mutate(cluster = as.factor(cluster) %>% fct_lump_min(bioregion_cutoff))

@@

# Map phylogenetic clusters to grid cells
clusters_phy <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = phylo_cluster)

cluster_nodes_phy_tbl <- map_df(unique(clusters_phy$cluster), ~map_cluster_to_nodes(dendro_phy, clusters_phy, .)) %>%
  # Lump regions with fewer grid-cells than cutoff
  mutate(cluster = as.factor(cluster) %>% fct_lump_min(bioregion_cutoff))

### 2021-09-06 ms/manuscript.Rmd
Don't hard-code bioregion lumping cutoff

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "aic_env_repro",
  "binary_sig_results",
  "biodiv_ferns_cent",
  "biodiv_ferns_spatial",
  "broad_alignment_list",
  "comm_ferns",
  "comm_ferns_full",
  "csl_file",
  "deer_range",
  "fern_traits",
  "green_list",
  "japan_fern_tree",
  "japan_map_points",
  "japan_pterido_tree",
  "japan_rbcL",
  "japan_shp",
  "k_phylogeny",
  "k_taxonomy",
  "lat_span_summary",
  "lrt_results",
  "model_fits",
  "model_params",
  "ms_functions",
  "occ_point_data_summary",
  "phy_sig_results",
  "plastome_calibration_dates",
  "plastome_tree",
  "ppgi",
  "protected_areas",
  "refs_other_yaml",
  "refs_yaml",
  "repro_data",
  "signif_cells_protected_area",
  "signif_cells_deer_danger",
  "template_file",
  "traits_summary",
  "biodiv_ferns_spatial_lumped"
))
```

@@

**`r figure("bioregions")`**. Bioregions of the ferns of Japan. (a), taxonomic bioregions. (b), phylogenetic bioregions. Bioregions determined by clustering taxonomic (Sørensen) or phylogenetic (PhyloSor) distances between grid-cells. Bioregions with three or fewer grid-cells are lumped into the "Other" category.

>>>>

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "aic_env_repro",
  "binary_sig_results",
  "biodiv_ferns_cent",
  "biodiv_ferns_spatial",
  "broad_alignment_list",
  "comm_ferns",
  "comm_ferns_full",
  "csl_file",
  "deer_range",
  "fern_traits",
  "green_list",
  "japan_fern_tree",
  "japan_map_points",
  "japan_pterido_tree",
  "japan_rbcL",
  "japan_shp",
  "k_phylogeny",
  "k_taxonomy",
  "lat_span_summary",
  "lrt_results",
  "model_fits",
  "model_params",
  "ms_functions",
  "occ_point_data_summary",
  "phy_sig_results",
  "plastome_calibration_dates",
  "plastome_tree",
  "ppgi",
  "protected_areas",
  "refs_other_yaml",
  "refs_yaml",
  "repro_data",
  "signif_cells_protected_area",
  "signif_cells_deer_danger",
  "template_file",
  "traits_summary",
  "biodiv_ferns_spatial_lumped",
  "bioregion_cutoff"
))
```

@@

**`r figure("bioregions")`**. Bioregions of the ferns of Japan. (a), taxonomic bioregions. (b), phylogenetic bioregions. Bioregions determined by clustering taxonomic (Sørensen) or phylogenetic (PhyloSor) distances between grid-cells. Bioregions each consisting of fewer than `r english2(bioregion_cutoff)` grid-cells are lumped into the "Other" category.
